%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
\usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\usepackage{tikz}

\newcommand{\ExternalLink}{
    \tikz[x=1.2ex, y=1.2ex, baseline=-0.05ex]{% 
        \begin{scope}[x=1ex, y=1ex]
            \clip (-0.1,-0.1) 
                --++ (-0, 1.2) 
                --++ (0.6, 0) 
                --++ (0, -0.6) 
                --++ (0.6, 0) 
                --++ (0, -1);
            \path[draw, 
                line width = 0.5, 
                rounded corners=0.5] 
                (0,0) rectangle (1,1);
        \end{scope}
        \path[draw, line width = 0.5] (0.5, 0.5) 
            -- (1, 1);
        \path[draw, line width = 0.5] (0.6, 1) 
            -- (1, 1) -- (1, 0.6);
        }
    }

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Harry Zhong} \\ \vspace{1pt}
    \small +61403041075 $|$ \href{mailto:h.zhong2687@gmail.com}{\underline{h.zhong2687@gmail.com}} $|$ 
    \href{https://www.linkedin.com/in/harry2687/}{\underline{linkedin.com/in/harry2687}} $|$
    \href{https://github.com/harry2687/}{\underline{github.com/harry2687}} $|$
    \href{https://harryz.netlify.app/}{\underline{harryz.netlify.app}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Curtin University}{Bentley, WA}
      {Bachelor of Science (Actuarial Science) (Honours), CWA: 84\%}{Feb 2019 -- Jun 2023}
    \resumeSubheading
      {Actuaries Institute}{Perth, WA}
      {Actuary Program (AIAA)}{Jul 2023 -- Oct 2023}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Data Analyst}{Nov 2022 -- Present}
      {EBM Insurance \& Risk}{Perth, WA}
      \resumeItemListStart
        \resumeItem{Gained a strong understanding of data analysis principles (relational databases, query languages, modelling) and applied them to a broad range of financial and insurance applications (financial reporting, scenario analysis, cashflow projection).}
        \resumeItem{Managed income forecast project which used statistical techniques in \textbf{R} to predict future income for financial reporting.}
        \resumeItem{Key contributor to the internal development of data analysis applications using \textbf{SQL} and \textbf{R}.}
        \resumeItem{Introduced the use of \textbf{Shiny} applications for data visualisation and report distribution, and \textbf{Git} for version control in \textbf{R}.}
        \resumeItem{Modelled annual income of client portfolios in \textbf{Microsoft Excel} for discounted cash flow valuations.}
        \resumeItem{Delivered monthly income reports using \textbf{VBA} to automate repetitive tasks.}
      \resumeItemListEnd
      
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{\href{https://github.com/Harry2687/Gender-Prediction}{Gender Prediction - PyTorch}\ExternalLink} $|$ \emph{Python, PyTorch}}{2024}
          \resumeItemListStart
            \resumeItem{Used PyTorch to define and implement custom convolutional neural network used to classify facial features using the CelebA dataset.}
            \resumeItem{Tuned hyperparameters (batch size, kernel sizes, and layer composition) to optimise convergence speed and loss measure.}
            \resumeItem{Achieved 95\% accuracy in training and testing splits of dataset.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{\href{https://harryz.netlify.app/projects/spotify-analysis/}{Spotify Track Clustering}\ExternalLink} $|$ \emph{R, Spotify API}}{2024}
          \resumeItemListStart
            \resumeItem{Used R to extract Spotify streaming history along with Spotify's developer API to query track features.}
            \resumeItem{Used Spotify track features to apply k-means clustering algorithm to tracks in streaming history.}
            \resumeItem{Implemented brute force method of feature selection and parallel processing to optimise computation time.}
            \resumeItem{Visualised clustering results and streaming trends using Shiny applications.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{\href{https://github.com/Harry2687/Messenger-Analysis}{Messenger Chat Clustering - Gensim LDA}\ExternalLink} $|$ \emph{Python, Gensim}}{2024}
          \resumeItemListStart
            \resumeItem{Used Python to extract Facebook Messenger chat data stored as JSON files.}
            \resumeItem{Implemented latent Dirichlet allocation (LDA) using the gensim module.}
            \resumeItem{Tuned the 3 hyperparameters of LDA using coherence score as a measure of model performance.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{\href{https://www.researchgate.net/publication/372915363_Comparing_Stochastic_and_Constant_Volatility_Returns_Distributions_using_the_Heston_Model}{Honours Dissertation - Stochastic Volatility}\ExternalLink} $|$ \emph{R}}{2023}
          \resumeItemListStart
            \resumeItem{Used stochastic modelling to compare constant and stochastic volatility under geometric Brownian motion based on independent research.}
            \resumeItem{Used R to optimise parameterisation and simulation via parallel processing.}
            \resumeItem{Completed written research report and presented seminar presentation to supervisors.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd



%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: R, Python, SQL, Visual Basic} \\
     \textbf{Software}{: Excel, Power BI} \\
     \textbf{Developer Tools}{: Git, GitHub, VS Code, R Studio} \\
     \textbf{Libraries (R)}{: ggplot2, dplyr, tidyr, purrr} \\
     \textbf{Libraries (Python)}{: pandas, NumPy, Matplotlib, PyTorch}
    }}
 \end{itemize}


%-------------------------------------------
\end{document}
